\documentclass[a4paper, oneside]{discothesis}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DOCUMENT METADATA

\title{Project Description}
\thesistype{Bachelor's Thesis \\ Course Unit: 252-0500-00}

\author{Florian Bütler}
\email{flbuetle@ethz.ch}

\institute{Chair of Information Technology and Education \\[2pt]
ETH Zürich}

\supervisors{Prof.\ Juraj Hromkovič}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\frontmatter % do not remove this line
\maketitle

\cleardoublepage

\mainmatter % do not remove this line

\section*{Topic}

This thesis is about a computer-based learning environment aimed for students at the 3rd and 4th grade level. It supports teachers in teaching their students a selected number of topics in computer science.

\section*{Motivation and Background}

Computer Science has been taking over our daily life in every aspect. With this also the need of the ability to understand how Computers work and think increased enormously. To satisfy this need in the long term Computer Science was included in the Swiss curriculum with the Lehrplan 21.
The goal of the Lehrplan 21 is to teach the students the basic concepts of Computer Science and give them the ability to use those concepts for problem solving. Therefore the main goal here is to implement tasks in a computer-based learning environment that teach a chosen subset of those concepts.

\section*{Goals of the Thesis}

This thesis should implement chosen tasks and riddles from “einfach INFORMATIK 3/4” about:
\begin{itemize}
  \item representing information with symbols,
  \item protecting data and keeping information secret and
  \item learning from data
\end{itemize}
at 3rd and 4th grade level.
Along with solving tasks and riddles about the mentioned topics the ability of reading, writing, counting and calculating is trained as well.

\section*{Deliverables}

The student is expected to manage the project, comply with rigorous scientific standards,
and to apply sound software engineering procedures in order to successfully design, develop
and test the platform.

\section*{Grading Criteria}

The Bachelor Thesis will be graded according to the \emph{Guidelines Bachelor’s Thesis}\cite{BscThesisGuidelines}.

% This displays the bibliography for all cited external documents. All references have to be defined in the file references.bib and can then be cited from within this document.
\bibliographystyle{IEEEtran}
\bibliography{references}

% This creates an appendix chapter, comment if not needed.
% \appendix
% \chapter{First Appendix Chapter Title}

\end{document}